### 2014-11-12 nqueens.tex
Remove unneeded subfloats.

Since computation goes from the top row to the bottom row, not all
placements of nodes to threads performane equally. This is especially
true because the bottom rows tend to perform the most work. The best
placement is then to split the board vertically so each thread gets
the same number of columns. Our experiments show that, on a shared
memory system, it does not matter much if we start with a bad
placement since node stealing overcomes those issues by load balancing
dynamically. However, we noticed interesting cache effects when
prioritizing nodes in bottom rows.\snote{Expand on this?  What are
they?} The N Queens program builds and shares lists representing valid
board states and needs to iterate over those lists often when checking
if a new position does not invalidate a state.  We thus used
coordination axioms \texttt{set-default-priority(A, X)}
and \texttt{set-cpu(A, vertical(X, Y))}, where \texttt{X} is the row
number (0 is the top row) \texttt{Y} is the column number to
prioritize the evaluation of squares at the XXXX of the board and to
keep board configurations in the same cache. \snote{check the previous}

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=5.5cm]{results/8queens-13.png}}
   \end{center}
   \scap{results:nqueens}{Experimental results for the 13 Queens program.
   Coordination works best when 1 column is assigned to one thread and bottom
   rows have higher priority.}
\end{topfig}

>>>>

Since computation goes from the top row to the bottom row, not all
placements of nodes to threads performane equally. This is especially
true because the bottom rows tend to perform the most work. The best
placement is then to split the board vertically so each thread gets
the same number of columns with axiom \texttt{set-cpu(A, vertical(X, Y)}, where
\texttt{X} and \texttt{Y} are the coordinates of the board. Our experiments show that, on a shared
memory system, it does not matter much if we start with a bad
placement since node stealing overcomes those issues by load balancing
dynamically.  However, the N Queens program incrementally builds and shares lists representing
valid board states that are transmitted from top to bottom.
In order to improve memory locality we should then manipulate board
states that share a significant number of elements because each board state
needs to be iterated before extended with a new position.
To accomplish this, we used coordination axioms \texttt{set-default-priority(A,
X)}, where \texttt{X} is the row number (0 is the top row) in order to
prioritize the evaluation of squares closer to the bottom of the board.

@@

\begin{topfig}
   \begin{center}
      \includegraphics[width=5.5cm]{results/8queens-13.png}
   \end{center}
   \scap{results:nqueens}{Experimental results for the 13 Queens program.
   Coordination works best when 1 column is assigned to one thread and bottom
   rows have higher priority.}
\end{topfig}
